Meta-analysis

### 2019-11-05 04_Prep_data.Rmd
Spray management cluster code correction

slim_PM_dat %>%
  mutate(
    spray_management = case_when(
       fungicide_timing_1 < 0 &
          is.na(fungicide_application_2) &
          is.na(fungicide_application_3) ~ "Early",
       fungicide_timing_1 >= 0 &
          fungicide_timing_1 < 4 &
          is.na(fungicide_application_2) &
          is.na(fungicide_application_3) ~ "Recommended",
      fungicide_timing_1 >= 4 &
          is.na(fungicide_application_2) &
          is.na(fungicide_application_3) ~ "Late",
      fungicide_timing_1 < 0 &
          !is.na(fungicide_application_2) ~ "Early_plus",
       fungicide_timing_1 >= 0 &
          fungicide_timing_1 < 4 &
          !is.na(fungicide_application_2) ~ "Recommended_plus",
      fungicide_timing_1 >= 4 &
          !is.na(fungicide_application_2) ~ "Late_plus",
      TRUE ~ NA_character_
    )
  )

>>>>

slim_PM_dat <- slim_PM_dat %>%
   mutate(
    spray_management = case_when(
       fungicide_timing_1 < 0 &
          is.na(fungicide_application_2) &
          is.na(fungicide_application_3) ~ "Early",
       fungicide_timing_1 >= 0 &
          fungicide_timing_1 < 4 &
          is.na(fungicide_application_2) &
          is.na(fungicide_application_3) ~ "Recommended",
      fungicide_timing_1 >= 4 &
          is.na(fungicide_application_2) &
          is.na(fungicide_application_3) ~ "Late",
      fungicide_timing_1 < 0 &
          !is.na(fungicide_application_2) ~ "Early_plus",
       fungicide_timing_1 >= 0 &
          fungicide_timing_1 < 4 &
          !is.na(fungicide_application_2) ~ "Recommended_plus",
      fungicide_timing_1 >= 4 &
          !is.na(fungicide_application_2) ~ "Late_plus"
    )
  )
